ES Models: Random Forest

### 2025-03-26 randomforest_kl.Qmd
update site

     r2 = `{r} round(pollinators_base.rf$r.squared, 3)`
     OOB MSE = `{r} round(pollinators_base.rf$prediction.error, 3)`

@@

     r2 = `{r} round(pollinators_margin.rf$r.squared, 3)`
     OOB MSE = `{r} round(pollinators_margin.rf$prediction.error, 3)`

@@

     r2 = `{r} round(n_export_base.rf$r.squared, 3)`
     OOB MSE = `{r} round(n_export_base.rf$prediction.error, 3)`

@@

     r2 = `{r} round(n_export_margin.rf$r.squared, 3)`
     OOB MSE = `{r} round(n_export_margin.rf$prediction.error, 3)`

@@

     r2 = `{r} round(sed_export_base.rf$r.squared, 3)`
     OOB MSE = `{r} round(sed_export_base.rf$prediction.error, 3)`

@@

     r2 = `{r} round(sed_export_margin.rf$r.squared, 3)`
     OOB MSE = `{r} round(sed_export_margin.rf$prediction.error, 3)`

@@

     r2 = `{r} round(qb_base.rf$r.squared, 3)`
     OOB MSE = `{r} round(qb_base.rf$prediction.error, 3)`

@@

     r2 = `{r} round(qb_margin.rf$r.squared, 3)`
     OOB MSE = `{r} round(qb_margin.rf$prediction.error, 3)`

>>>>

     r2 = `r round(pollinators_base.rf$r.squared, 3)`
     OOB MSE = `r round(pollinators_base.rf$prediction.error, 3)`

@@

     r2 = `r round(pollinators_margin.rf$r.squared, 3)`
     OOB MSE = `r round(pollinators_margin.rf$prediction.error, 3)`

@@

     r2 = `r round(n_export_base.rf$r.squared, 3)`
     OOB MSE = `r round(n_export_base.rf$prediction.error, 3)`

@@

     r2 = `r round(n_export_margin.rf$r.squared, 3)`
     OOB MSE = `r round(n_export_margin.rf$prediction.error, 3)`

@@

     r2 = `r round(sed_export_base.rf$r.squared, 3)`
     OOB MSE = `r round(sed_export_base.rf$prediction.error, 3)`

@@

     r2 = `r round(sed_export_margin.rf$r.squared, 3)`
     OOB MSE = `r round(sed_export_margin.rf$prediction.error, 3)`

@@

     r2 = `r round(qb_base.rf$r.squared, 3)`
     OOB MSE = `r round(qb_base.rf$prediction.error, 3)`

@@

     r2 = `r round(qb_margin.rf$r.squared, 3)`
     OOB MSE = `r round(qb_margin.rf$prediction.error, 3)`
